Universal Anonymous Signatures

### 2022-10-01 prism-backend/research/gsac/formal-uas.tex
Added back issuance unforgeability to fix issuance flaw. Updated rest of the paper. Proofs can be improved.

\begin{description}
\item[$\mathsf{H}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Sets of
  honest {\uid}s/{\iid}s/{\oid}s.
\item[$\mathsf{C}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Sets of
  corrupt {\uid}s/{\iid}s/{\oid}s.
\item[\UK,\IK,\OK.] Tables storing key pairs of users $(\upk,\usk)$, issuers
  $(\ipk,\isk)$, and openers $(\opk,\osk)$, indexable by \uid, \iid, and \oid,
  respectively. Issuers' public keys contain a \fissue function, and
  openers' public keys contain a \finsp function.
\item[\PUBUK,\PUBIK,\PUBOK and \PRVUK,\PRVIK,\PRVOK.] Shorthands referring to
  public keys of users, issuers or openers ($\mathsf{PXK}$) or their private
  keys ($\mathsf{SXK}$).
\item[\CRED.] Indexable by \cid, it stores
  tuples of the form $(\uid,\cred,\iid,\attrs,n,\lbrace (\cid_i,\iid_i)
  \rbrace_{i \in [n]})$, where \uid is the identifier of the owner of the
  credential, \cred (when available) is the credential itself, \iid is the
  identifier of the credential issuer, \attrs are the attributes included in
  \cred, $n$ is the number of credentials used to support this request, and
  $(\cid_i,\iid_i)$ for $i \in [n]$ are the corresponding credential and issuer
  identifiers. For notational convenience, we may use $\CRED[\scid]$
  to refer to $\CRED[\cid]$ for all {\cid}s in a set \scid. Also, when clear
  from context, we sometimes use $\CRED[\cid]$ (resp. $\CRED[\scid]$) to
  mean \cred (resp. \scred) in $\CRED[\cid] = (\cdot,\cred,\cdot,\cdot,
  \cdot,\cdot)$ (resp. $\CRED[\scid]$).
\item[\CCRED.] Like \CRED, but tracks challenge credentials.
\item[\OWNR.] When we write $\OWNR[\cid]$ we mean
  ``\uid such that $\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot)$'', or
  $\bot$ if there is no wuch \uid. We also use \OWNR over a set of {\cid}s
  (\scid). In that case, $\OWNR[\scid]$ returns $\bot$ if
  not all passed {\cid}s belong to the same \uid. Since $\bot$ is not a valid
  \uid, all conditions checking membership of the output of \OWNR to a list of
  users equal false if \OWNR returns $\bot$.
\item[\ATTR.] When we write $\ATTR[\cid]$ we mean
  ``\attrs such that $\CRED[\cid] = (\cdot,\cdot,\cdot,\attrs,\cdot,\cdot)$''.
\item[\ISR.] When we write $\ISR[\cid]$ we mean
  ``\iid such that $\CRED[\cid] = (\cdot,\cdot,\iid,\cdot,\cdot,\cdot)$''.
\item[\SIG.] Maintains signatures generated via the \SIGN oracle. Entries of
  this table are $(\oid,\scid,\sig,\Yeval,\msg,\feval)$ tuples, where \oid is
  the opener, \scid is the set of identifiers of the credentials used for
  signing, \feval is the signing evaluation function, and \sig and \msg are the
  produced signature and signed message.
\item[\CSIG.] Maintains challenge signatures output to the adversary in the
  signature anonymity game, and is indexable by challenge signatures \csig.
  Each entry contains also $\cuid_b$ and $\cscid_b$, respectively the challenge
  user  and credential identifiers set used to produce \csig; as well as the
  corresponding challenge user and credential set indexed by the complementary
  $1-b$; the signed message \msg and signing evaluation function \feval, the
  result of \feval, \Yeval, and the opener identifier \oid.
\end{description}

@@

{%\setlength\intextsep{\sep}
  \begin{figure*}[htp!]
    \centering
    \scalebox{0.85}{

      \begin{minipage}[t]{0.58\textwidth}

@@

        \procedure{$\ISSUE(\uid,\iid,\attrs,\siid=
          \lbrace \iid_i\rbrace_{i\in[n]})$}{%
          \pcif \uid \notin \CU \lor \iid \notin \HI: \pcreturn \bot \\          
          \langle \cdot, R \rangle \gets
          \langle \adv, 
          \Issue(\PRVIK[\iid],\siid,\attrs) \rangle \\
          (\cdot,\cdot,(\cidi,\cdot)) \gets R \\
          \pcif \CRED[(\cidi,\cdot)] \neq \bot \lor \CCRED[(\cidi,\cdot)]
          \neq \bot: \\
          \pcind \pcreturn \bot \\          
          \trans[(\cidi,\cdot)] \gets R \\
          \CRED[(\cidi,\cdot)] \gets (\uid,\cdot,\iid,\attrs,n,\lbrace(\cdot,
          \iid_i)
          \rbrace_{i\in[n]}) \\
          \pcreturn \top \\          
        }

@@

        \procedure{$\OBTAIN(\uid,\iid,\attrs,\lbrace (\cid_i,\iid_i)
          \rbrace_{i\in[n]})$}{%
          \pcif \uid \notin \HU \lor \iid \notin \CI: \pcreturn \bot \\
          \pcif \exists i \in [n]~\suchthat~\cid_i \in \CCRED: \pcreturn \bot \\
          \pcind \pcreturn \bot \\
          \langle \Cred, \cdot \rangle \gets
          \langle \Obtain(\UK[\uid],\PUBIK[\iid],\lbrace \cid_i\rbrace_{[n]},
          \attrs),\adv \rangle \\
          (\cid = (\cdot,\cidu), \cdot,\cdot,\cdot) \gets \Cred \\
          \pcif \CRED[(\cdot,\cidu)] \neq \bot \lor \CCRED[(\cidu,\cdot)] \neq
          \bot: \\          
          \CRED[(\cdot,\cidu)] \gets (\uid,\cred,\iid,\attrs,n,\lbrace(\cid_i,
          \iid_i) \rbrace_{i\in[n]}) \\
          \pcreturn \top \\
        }

        \procedure{$\OBTCHALb(\cuid_{0,1},\iid,\attrs,
          \stackrel{\cscid_{\lbrace 0,1 \rbrace}}
          {\pcbox{\lbrace(\ccid_{0,i},\ccid_{1,i})\rbrace_{i\in[n]}}})$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \CI: \pcreturn \bot \\
          \pcif \exists i\in[n]~\suchthat~
          \PUBIK[\cscid_{0,i}] \neq \PUBIK[\cscid_{1,i}]: \pcreturn \bot \\
          \pcif \pcfor d \in \bin,~ \exists \cid' \in \cscid_d~\suchthat~\cid'
          \in \CRED: \\
          \pcind \pcreturn \bot \\          
          \langle \Cred, \cdot \rangle \gets
          \langle \Obtain(\PRVUK[\cuid_b],\PUBIK[\iid],\cscid_b,\attrs),
          \adv \rangle \\
          (\cid = (\cidi,\cidu),\cdot,\cdot,\cdot) \gets \Cred \\
          \textrm{Parse}~\PUBIK[\iid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
          \pcif 0(\fissue(\PUBUK[\cuid_0],\cid,\attrs,\lbrace
          (\ccid_{0,i},\ATTR[\ccid_{0,i}])\rbrace_{i\in[n]})) \neq \\
          \pcind 0(\fissue(\PUBUK[\cuid_1],\cid,\attrs,\lbrace
          (\ccid_{1,i},\ATTR[\ccid_{1,i}])\rbrace_{i\in[n]})): \\
          \pcind \pcreturn \bot \\          
          \pcif \CRED[(\cdot,\cidu)] \neq \bot \lor
          \CCRED[(\cdot,\cidu)] \neq \bot: \pcreturn \bot \\          
          \CCRED[(\cdot,\cidu)] \gets (\cuid_b,\cred,\iid,\attrs,\cscid_b,\siid) \\
          \pcreturn \top \\
        }

@@

\begin{description}
\item[$\SimSetup(1^\secpar) \rightarrow (\parm,\trap)$.] Given a security
  parameter, outputs global parameters \parm whose distribution is
  indistinguishable to that produced by the \Setup algorithm, as well as a
  trapdoor \trap.
\item[$\ExtractIssue(\trap,\utrans) \rightarrow (\upk,\usk,\sCred=
  \lbrace(\cid_i,\attrs_i,\cred_i) \rbrace_{i \in [n]})$.]
  Receives trapdoor \trap and an $\langle \Obtain, \Issue \rangle$ transcript,
  and returns the credential set \sCred, if any, involved in the request. It
  requires honest issuers for the transcripts to be available. 
\item[$\ExtractSign(\trap,\opk,\lbrace \ipk_i \rbrace_{i \in [n]},\Sig,\msg,
  \feval) \rightarrow (\upk,\usk,\sCred=\lbrace(\cid_i,\attrs_i,\cred_i)
  \rbrace_{i \in [n]},\yeval^1,\yinsp)$.] Receives trapdoor \trap, signature
  \Sig over \msg and for \feval, opener public key \opk, and public keys
  $\ipk_i$ from the issuers of the credentials used to produce \Sig. It outputs
  the user secret key and credential set \sCred used to generate the signature,
  and the $\yeval^1$ and \yinsp values. For notational convenience, we overload
  this function and use \oid and \iid instead of the actual keys.
% \item[$\IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk)$.] Returns $1$ if
%   \cred has been issued over attributes $\attrs_{\cred}$ and for a user with
%   secret key \usk, by honest issuer with public key \ipk. Otherwise, it returns
%   $0$.

@@

\paragraph{Unforgeability.} In \UAS schemes, we need to prevent forging either
credential requests, or signatures. The latter is mostly a combination of the
unforgeability of AC schemes, and the traceability of GS schemes with verifiable
openings. However, issuance unforgeability is a direct consequence of allowing
proving arbitrary claims already when requesting credentials.

In more detail, issuance unforgeability captures that all the credentials issued
by an honest issuer meet the requirements set by the corresponding issuance
function. Moreover, any credential used to support a request needs to belong
to a known user. 
The adversary is required to output a credential identifier that must correspond
to an existing credential issuance interaction -- note that the transcript must
be available to us if it exists, as the issuer is honest. From this transcript,
we extract the witness used to compute the issuance function, which includes the
output of the issuance function claimed by the requestor, and the credential
identifiers of any used credential. The adversary wins if applying the output of
the issuance function applied to the extracted witness is not consistent, or if
the credential identifiers do not belong all to the same (known) user.

Signature unforgeability is a combination of known requirements in AC and
GS schemes. Namely, the adversary is required to output a valid signature, and
wins if the signature: (1) opens to a wrong value, or to a value that cannot be
processed by \Judge; (2), is not consistent with the expected $\Yeval =
(\yeval^0,\yeval^1)$ value; or (3), cannot be associated to credentials
owned by a known user.

We formalize the respective properties, \ExpForgeIssue and \ExpForgeSign, in
\figref{fig:exp-uas-unfor}.

@@

\begin{figure}[htp!]
  \centering
  \hspace*{-2em}
  \scalebox{0.85}{
    \begin{minipage}[t]{0.6\textwidth}
      \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
        \cid \gets \adv^{\Oforge}(\parm) \\
        \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot:
        \pcreturn 0 \\
        (\yissue,\utrans) \gets \trans[\cid];
        ((\cdot,\fissue),\cdot) \gets \PUBIK[\cid] \\        
        (\upk,\usk,\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i \in [n]}) \\
        \pcind \gets \ExtractIssue(\trap,\utrans) \\
        \pcreturn \OWNR[\lbrace\cid_i\rbrace_{i\in[n]}\cup\cid] \notin \HU \cup
        \CU~\lor \\
        \pcind \fissue(\upk,\ATTR[\cid],\lbrace (\cid_i,\attrs_i)
        \rbrace_{i\in[n]}) \neq \yissue        
      }      
    \end{minipage}    
    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering=on]{$\ExpForgeSign(1^\secpar)$}{%
        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
        (\oid,\siid,\Sig=(\sig,\tyeval^0),\msg,\feval) \gets \adv^{\Oforge}(\parm) \\
        \pcif \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
        \SIG[\uid]~\lor  \\
        \pcind \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0: \\
        \pcind \pcreturn 0 \\
        (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\Sig,\msg) \\
	(\upk,\cdot,\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i\in[n]},
        \tyeval^1,\tyinsp) % \pcskipln
        \\
        \pcind \gets \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
        (\yeval^0,\yeval^1) \gets \feval(\upk,\lbrace(\cid_i,\attrs_i)
        \rbrace_{i\in[n]}, \msg) \\
        \pcreturn \OWNR[\lbrace \cid_i \rbrace_{i\in[n]}] \notin
        \HU \cup \CU~\lor \\
        \pcind \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,
        \msg,\feval) = 0~\lor \\
        \pcind \yeval^0 \neq \tyeval^0 \lor \yeval^1 \neq \tyeval^1 \lor
        \yinsp \neq \tyinsp~\lor\\
        \pcind \finsp((\yeval^0,\yeval^1),\upk,\lbrace(\cid_i,\attrs_i)
        \rbrace_{i\in[n]},\msg) \neq \yinsp 
      }
    \end{minipage}
  }
  \caption{Unforgeability experiments in \UAS schemes.
    $\Oforge \gets \lbrace\OO,\HU,\CU\rbrace\GEN,\ISET,\lbrace\OO,\UU\rbrace
    \CORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN$.}
  \label{fig:exp-uas-unfor}
\end{figure}

@@

\begin{theorem}[Issuance unforgeability of \CUASGen]
  \label{thm:issue-forge-uas}
  \todo{Update}
  If the underlying NIZK used for \RelIss is zero-knowledge,
  simulation extractable and sound, then our \CUASGen construction satisfies
  issuance unforgeability as defined in \defref{def:issue-forge-uas}.
\end{theorem}

\begin{theorem}[Signing unforgeability of \CUASGen]
  \label{thm:sign-forge-uas}
  \todo{Update}
  If the underlying NIZK scheme for \RelSig is simulation
  extractable, the scheme for \RelIns is complete, the public key
  encryption algorithm is correct, and the \SBCM scheme is correct and one-more
  unforgeable, then our \CUASGen construction satisfies signing unforgeability
  as defined in \defref{def:sign-forge-uas}, except with negligible probability.
\end{theorem}

>>>>

\begin{description}
\item[$\mathsf{H}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Sets of
  honest {\uid}s/{\iid}s/{\oid}s.
\item[$\mathsf{C}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Sets of
  corrupt {\uid}s/{\iid}s/{\oid}s.
\item[\UK,\IK,\OK.] Tables storing key pairs of users $(\upk,\usk)$, issuers
  $(\ipk,\isk)$, and openers $(\opk,\osk)$, indexable by \uid, \iid, and \oid,
  respectively. Issuers' public keys contain a \fissue function, and
  openers' public keys contain a \finsp function.
\item[\PUBUK,\PUBIK,\PUBOK and \PRVUK,\PRVIK,\PRVOK.] Shorthands referring to
  public keys of users, issuers or openers ($\mathsf{PXK}$) or their private
  keys ($\mathsf{SXK}$).
\item[\CRED.] Indexable by \cid, it stores
  tuples of the form $(\uid,\cred,\iid,\attrs,n,\lbrace (\cid_i,\iid_i)
  \rbrace_{i \in [n]})$, where \uid is the identifier of the owner of the
  credential, \cred (when available) is the credential itself, \iid is the
  identifier of the credential issuer, \attrs are the attributes included in
  \cred, $n$ is the number of credentials used to support this request, and
  $(\cid_i,\iid_i)$ for $i \in [n]$ are the corresponding credential and issuer
  identifiers. For notational convenience, we may use $\CRED[\scid]$
  to refer to $\CRED[\cid]$ for all {\cid}s in a set \scid. Also, when clear
  from context, we sometimes use $\CRED[\cid]$ (resp. $\CRED[\scid]$) to
  mean \cred (resp. \scred) in $\CRED[\cid] = (\cdot,\cred,\cdot,\cdot,
  \cdot,\cdot)$ (resp. $\CRED[\scid]$).
\item[\CCRED.] Like \CRED, but tracks challenge credentials.
\item[\OWNR.] When we write $\OWNR[\cid]$ we mean
  ``\uid such that $\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot)$'', or
  $\bot$ if there is no such \uid. We also use \OWNR over a set of {\cid}s
  (\scid). In that case, $\OWNR[\scid]$ returns $\bot$ if
  not all passed {\cid}s belong to the same \uid. Since $\bot$ is not a valid
  \uid, all conditions checking membership of the output of \OWNR to a list of
  users equal false if \OWNR returns $\bot$.
\item[\ATTR.] When we write $\ATTR[\cid]$ we mean
  ``\attrs such that $\CRED[\cid] = (\cdot,\cdot,\cdot,\attrs,\cdot,\cdot)$''.
\item[\ISR.] When we write $\ISR[\cid]$ we mean
  ``\iid such that $\CRED[\cid] = (\cdot,\cdot,\iid,\cdot,\cdot,\cdot)$''.
\item[\SIG.] Maintains signatures generated via the \SIGN oracle. Entries of
  this table are $(\oid,\scid,\sig,\Yeval,\msg,\feval)$ tuples, where \oid is
  the opener, \scid is the set of identifiers of the credentials used for
  signing, \feval is the signing evaluation function, and \sig and \msg are the
  produced signature and signed message.
\item[\CSIG.] Maintains challenge signatures output to the adversary in the
  signature anonymity game, and is indexable by challenge signatures \csig.
  Each entry contains also $\cuid_b$ and $\cscid_b$, respectively the challenge
  user  and credential identifiers set used to produce \csig; as well as the
  corresponding challenge user and credential set indexed by the complementary
  $1-b$; the signed message \msg and signing evaluation function \feval, the
  result of \feval, \Yeval, and the opener identifier \oid.
\end{description}

@@

{%\setlength\intextsep{\sep}
  \begin{figure*}[htp!]
    \centering
    \scalebox{0.85}{
      \hspace*{-2em}
      \begin{minipage}[t]{0.58\textwidth}

@@

        \procedure{$\ISSUE(\uid,\iid,\attrs,\siid=
          \lbrace \iid_i\rbrace_{i\in[n]})$}{%
          \pcif \uid \notin \CU \lor \iid \notin \HI: \pcreturn \bot \\
          \langle \cdot, R \rangle \gets
          \langle \adv, 
          \Issue(\PRVIK[\iid],\siid,\attrs) \rangle \\
          (\cdot,\cdot,\cid=(\cidi,\cdot)) \gets R \\
          \pcif \CRED[(\cidi,\cdot)] \neq \bot \lor \CCRED[(\cidi,\cdot)]
          \neq \bot: \\
          \pcind \pcreturn \bot \\          
          \trans[\cid] \gets R \\
          \CRED[\cid] \gets (\uid,\cdot,\iid,\attrs,n,\lbrace(\cid_i,
          \iid_i)
          \rbrace_{i\in[n]}) \\
          \pcreturn \top \\          
        }

@@

        \procedure{$\OBTAIN(\uid,\iid,\attrs,\lbrace (\cid_i,\iid_i)
          \rbrace_{i\in[n]})$}{%
          \pcif \uid \notin \HU \lor \iid \notin \CI: \pcreturn \bot \\
          \pcif \exists i \in [n]~\suchthat~\cid_i \in \CCRED: \pcreturn \bot \\
          \pcind \pcreturn \bot \\
          \langle \Cred, \cdot \rangle \gets
          \langle \Obtain(\UK[\uid],\PUBIK[\iid],\lbrace \cid_i\rbrace_{[n]},
          \attrs),\adv \rangle \\
          (\cid = (\cdot,\cidu), \cdot,\cdot,\cdot) \gets \Cred \\
          \pcif \CRED[(\cdot,\cidu)] \neq \bot \lor \CCRED[(\cidu,\cdot)] \neq
          \bot: \pcreturn \bot \\          
          \CRED[\cid] \gets (\uid,\cred,\iid,\attrs,n,\lbrace(\cid_i,
          \iid_i) \rbrace_{i\in[n]}) \\
          \pcreturn \top
        }

        \procedure{$\OBTCHALb(\cuid_{0,1},\iid,\attrs,
          \stackrel{\cscid_{\lbrace 0,1 \rbrace}}
          {\lbrace(\pcbox{(\ccid_{0,i},\ccid_{1,i})}},\iid_i)\rbrace_{i\in[n]})$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \CI: \pcreturn \bot \\
          \pcif \exists i\in[n]~\suchthat~
          \PUBIK[\cscid_{0,i}] \neq \PUBIK[\cscid_{1,i}]: \pcreturn \bot \\
          \pcif \pcfor d \in \bin,~ \exists \cid' \in \cscid_d~\suchthat~\cid'
          \in \CRED: \\
          \pcind \pcreturn \bot \\          
          \langle \Cred, \cdot \rangle \gets
          \langle \Obtain(\PRVUK[\cuid_b],\PUBIK[\iid],\cscid_b,\attrs),
          \adv \rangle \\
          (\cid = (\cidi,\cidu),\cdot,\cdot,\cdot) \gets \Cred \\
          \textrm{Parse}~\PUBIK[\iid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
          \pcif 0(\fissue(\PUBUK[\cuid_0],\cid,\attrs,\lbrace
          (\ccid_{0,i},\ATTR[\ccid_{0,i}])\rbrace_{i\in[n]})) \neq \\
          \pcind 0(\fissue(\PUBUK[\cuid_1],\cid,\attrs,\lbrace
          (\ccid_{1,i},\ATTR[\ccid_{1,i}])\rbrace_{i\in[n]})): \\
          \pcind \pcreturn \bot \\          
          \pcif \CRED[(\cdot,\cidu)] \neq \bot \lor
          \CCRED[(\cdot,\cidu)] \neq \bot: \pcreturn \bot \\          
          \CCRED[\cid] \gets (\cuid_b,\cred,\iid,\attrs, n,
          \lbrace(\ccid_{b,i},\iid_i)\rbrace_{i\in[n]}) \\
          \pcreturn \top
        }

@@

\begin{description}
\item[$\SimSetup(1^\secpar) \rightarrow (\parm,\trap)$.] Given a security
  parameter, outputs global parameters \parm whose distribution is
  indistinguishable to that produced by the \Setup algorithm, as well as a
  trapdoor \trap.
\item[$\ExtractIssue(\trap,\utrans) \rightarrow (\upk,\usk,\sCred=
  \lbrace(\cid_i,\attrs_i,\cred_i) \rbrace_{i \in [n]},
  \Cred=(\cid,\attrs,\cred))$.]
  Receives trapdoor \trap and a valid $\langle \Obtain, \Issue \rangle$
  transcript \utrans. It outputs the credential \Cred issued as a result of the
  interaction in \utrans, along with the involved user key pair $(\upk,\usk)$
  and, if any, the credential set \sCred used to request \Cred.
\item[$\ExtractSign(\trap,\Sig) \rightarrow
  (\upk,\usk,\sCred=\lbrace(\cid_i,\attrs_i,\cred_i)
  \rbrace_{i \in [n]},\yeval^1,\yinsp)$.] Receives trapdoor \trap and a valid
  signature \Sig. It outputs the user secret key and credential set \sCred used
  to generate the signature, and the $\yeval^1$ and \yinsp values. 
% \item[$\IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk)$.] Returns $1$ if
%   \cred has been issued over attributes $\attrs_{\cred}$ and for a user with
%   secret key \usk, by honest issuer with public key \ipk. Otherwise, it returns
%   $0$.

@@

\paragraph{Unforgeability.} In \UAS schemes, we need to prevent forging either
credential requests, and signatures. The latter is mostly a combination of the
unforgeability of AC schemes, and the traceability of GS schemes with verifiable
openings. However, the need for issuance unforgeability is a consequence of
allowing to support credential requests with previously obtained credentials --
functionality which, to the best of our knowledge, \UAS is the first scheme
to support. In both cases, it is necessary to assume honest issuers.

Signature unforgeability, \ExpForgeSign, is mainly a combination (and
generalisation) of known requirements in AC and GS schemes. Namely, the
adversary is required to output a valid signature, from which we extract the
user key pair, credentials, $\yeval^1$ and \yinsp values used to generate the
signature. The adversary wins if the signature: (1) opens to a wrong value, or
to a value that cannot be processed by \Judge; (2), is not consistent with the
expected $\Yeval = (\yeval^0,\yeval^1)$ value; or (3), cannot be associated to
credentials owned by a known user. Here, we again need to assume honest issuers.
Otherwise, it is trivial for the adversary to produce untraceable credentials
(i.e., that do not appear in any ``log'') which then evaluate to any desired
value when used to generate a signature.

While it may seem enough to check that no valid signature can be created from
forged credentials (i.e., credentials that did not meet their issuance policy,
or are not bound to a known user), note that allowing credentials to
endorse further credential requests makes this argument insufficient. For
instance, if we only check the credentials involved in signature generation, it
is perfectly possible that a forged credential is used to obtain a legitimate
one, and then use the latter to finally create a valid signature -- concretly,
such misbehaviour is not prevented by \ExpForgeSign.

We thus extend unforgeability of signatures with issuance unforgeability,
\ExpForgeIssue. It captures that all honestly issued credentials meet the
requirements set by the corresponding issuer, and that any further credential
involved in the request is bound to the same known user. For this, we allow the
adversary \adv~to interact with the oracles (restricted to honest issuers).
Eventually, \adv~is challenged to output a credential identifier from which we
extract the actual witnesses used in the credential request associated to \cid.
\adv~wins if the issuance function, applied to the extracted values, does not
meet the expected output, or if not all of the credentials (if any) used to
support the request belong to a same (known) user. Note that the issuance
transcript associated to \cid must exist, as we unavoidably need to restrict to
honest issuers. Indeed, a dishonest issuer cannot be trusted to enforce any
policy, nor to properly keep all transcripts. In practice, this means that
dishonest issuers can create arbitrary credentials.

We formalize both properties in \figref{fig:exp-uas-unfor}.

@@

\begin{figure}[htp!]
  \centering
  \hspace*{-2em}
  \scalebox{0.85}{
    \begin{minipage}[t]{0.6\textwidth}
      \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
        % (\Cred,\uid,\iid,\oid,\feval,\msg) \gets \adv^{\Oforge}(\parm) \\
        % \Sig \gets \Sign(\PRVUK[\uid],\PUBOK[\oid],\Cred,\msg,\feval) \\
        % \pcif \Verify(\PUBOK[\oid],\PUBIK[\iid],\Sig,\msg,\feval) = 0: \\
        % \pcind \pcreturn 0 \\
        % (\upk,\usk, (\cid,\attrs,\cdot), \cdot, \cdot) \\
        % \pcind \gets \ExtractSign(\trap,\oid,\iid,\Sig,\msg,\feval) \\
        % \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot: \pcreturn 1 \\
        % (\yissue,\cdot) \gets \trans[\cid];
        % ((\cdot,\fissue),\cdot) \gets \PUBIK[\cid] \\
        % \pcif \nexists \lbrace (\cid_i,\attrs_i) \rbrace_{i\in[n]}
        % \in \CRED[\uid]~\suchthat \\
        % \pcind \fissue(\upk,\cid,\attrs,
        % \lbrace (\cid_i,\attrs_i) \rbrace_{i\in[n]}) = \yissue: \\
        % \pcind \pcreturn 1
        % 
        % ((\upk_1,r_1,\Ccom_1),\dots,(\upk_l,r_l,\Ccom_l),\st) \\
        % \pcind \gets \adv^{\HUGEN,\CUGEN}(\texttt{choose},\parm) \\
        % \pcif \exists i\in[l]~\suchthat~\forall \uid,
        % \upk_i \neq \PUBUK[\uid]:  \\
        % \pcind \pcreturn 0 \\
        % \cid \gets \adv^{\Oforge}(\texttt{forge},\st,\parm) \\
        \cid \gets \adv^{\Oforge}(\parm) \\
        \pcif \ISR[\cid] \notin \HI \lor \trans[\cid] = \bot: \pcreturn 0 \\
        (\utrans,\yissue) \gets \trans[\cid] \\
        (\upk,\cdot,\lbrace (\cid_i,\attrs_i) \rbrace_{i\in[n]},\cdot,\attrs,
        \cdot) \gets \ExtractIssue(\trap,\utrans) \\
        \textrm{Let $\scid \gets \lbrace \cid_i \rbrace_{i\in[n]} \cup
          \lbrace \cid \rbrace$} \\
        \pcreturn \OWNR[\scid] \notin \HU \cup \CU~\lor \\
        \pcind \fissue(\upk,\cid,\attrs,\lbrace (\cid_i,\attrs_i)\rbrace_{i\in[n]})
        \neq \yissue
      }      
    \end{minipage}    
    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering=on]{$\ExpForgeSign(1^\secpar)$}{%
        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
        (\oid,\siid,\Sig=(\sig,\tyeval^0),\msg,\feval) \gets \adv^{\Oforge}(\parm) \\
        \pcif \exists \iid \in \siid~\suchthat~\iid \notin \HI \lor
        \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
        \SIG[\uid]~\lor  \\
        \pcind \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0: \\
        \pcind \pcreturn 0 \\
        (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\Sig,\msg) \\
	(\upk,\usk,\lbrace(\cid_i,\attrs_i,\cred_i)\rbrace_{i\in[n]},
        \tyeval^1,\tyinsp) % \pcskipln
        \\
        \pcind \gets \ExtractSign(\trap,\Sig) \\
        (\yeval^0,\yeval^1) \gets \feval(\upk,\lbrace(\cid_i,\attrs_i)
        \rbrace_{i\in[n]}, \msg) \\
        \pcreturn \OWNR[\lbrace \cid_i \rbrace_{i\in[n]}] \notin
        \HU \cup \CU~\lor \\
        \pcind \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,
        \msg,\feval) = 0~\lor \\
        \pcind \yeval^0 \neq \tyeval^0 \lor \yeval^1 \neq \tyeval^1 \lor
        \yinsp \neq \tyinsp~\lor\\
        \pcind \finsp((\yeval^0,\yeval^1),\upk,\lbrace(\cid_i,\attrs_i)
        \rbrace_{i\in[n]},\msg) \neq \yinsp 
      }
    \end{minipage}
  }
  \caption{Unforgeability experiments in \UAS schemes.
    $\Oforge \gets \lbrace\OO,\HU,\CU\rbrace\GEN,\ISET,\lbrace\OO,\UU\rbrace
    \CORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN$. % In line 10 of \ExpForgeIssue, we
    % slightly abuse notation to denote that user \uid does not own a set of
    % credentials with {\cid}s and attributes equal to $\lbrace (\cid_i,\attrs_i)
    % \rbrace_{i\in[n]}$.
  }
  \label{fig:exp-uas-unfor}
\end{figure}

@@

\begin{theorem}[Issuance unforgeability of \CUASGen]
  \label{thm:issue-forge-uas}  
  If the underlying NIZK used for \RelIss is simulation extractable, and the
  underlying \SBCM scheme is correct, then our \CUASGen construction satisfies
  issuance unforgeability as defined in \defref{def:issue-forge-uas}.
\end{theorem}

\begin{theorem}[Signature unforgeability of \CUASGen]
  \label{thm:sign-forge-uas}
  If the underlying NIZK scheme for \RelSig is simulation extractable, the
  scheme for \RelIns is complete, the public key encryption algorithm is
  correct, and the \SBCM scheme is correct and one-more unforgeable, then our
  \CUASGen construction satisfies signing unforgeability as defined in
  \defref{def:sign-forge-uas}, except with negligible probability.
\end{theorem}
